Atypical Lyman-$\alpha$ emission in a dwarf galaxy via multiphase gas and rotation.

### 2017-02-07 paper/letter.tex
updated sections
updated intro

The first generation of galaxies trace our cosmic origins. 
They were the first steps in the evolution of galaxies such as the Milky
Way. 
In the standard Big Bang cosmology the only chemical elements that
were created in the nucleosynthesis process were Hydrogen, Helium and
Lithium.  
Heavier elements must have been created in stellar evolution process. 
Therefore, we expect the first generation of
galaxies to be metal free and rich in Hydrogen. 
This kind of primordial galaxies have not been detected yet. 
However, dwarf star forming galaxies with a low metallicity content
are seen as templates to understand the early galaxy evolution process.

Almost fifty years ago \citep{PartridgePeebles} it was realized that
young galaxies could be detected through a strong Lyman-$\alpha$ line
emission.

@@

We computed the projected half-luminosity radius to be $R_s=1.5\pm0.1$ kpc 
from the surface intensity profiles reported by.
\citep{2003A&A...410..481N}. 
Assuming spherical geometry, one can translate this value into a 3D
half-luminosity radius of $r_s=3R_s/2=2.25$ kpc.

@@

@@

\subsection{Rotation}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.7\textwidth]{CLARA-TOL-main.pdf}
\caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.} 
\end{center}
\end{figure*}

@@

>>>>

Primordial galaxies have not been detected yet. 
However, dwarf star forming galaxies with a low metallicity content
are seen as templates to understand the early galaxy evolution process. 
Almost fifty years ago \citep{PartridgePeebles} it was realized that
young galaxies could be detected through a strong Lyman-$\alpha$ line
emission.

@@

We computed the projected half-luminosity radius to be $R_s=1.5\pm0.1$ kpc 
from the surface intensity profiles reported by \citep{2003A&A...410..481N}. 
Assuming spherical geometry, one can translate this value into a 3D
half-luminosity radius of $r_s=3R_s/2=2.25$ kpc.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.6\textwidth]{CLARA-TOL-main.pdf}
\caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
  Dots correspond to the observational data. The line shows the results
of our best model from a full radiative transfer simulation both for
the rotation and multiphase models.} 
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase model\label{multiphaseresults}}
\end{center}
\end{figure*}

@@

\subsection{Bulk Rotation}

@@

@@

\section*{Acknowledgments}
